---
title: "Final Prject Preliminary EDA"
author: "Jiarui Fan"
Date: "11/15/2020"
output: html_notebook
---
```{r}
# clean up R environment
rm (list = ls())
# load some packages
library(readr)
library(tidyverse)
library(DataComputing)
library(ggplot2)
library(tidyr)
library(lubridate)
```
## 1: Which is the Most Popular Ramen Product?

### Data source
[Ramen Ratings | Kaggle](https://www.kaggle.com/residentmario/ramen-ratings)

```{r}
RamenFile<- file.choose()
```
```{r}
RamenData<- 
  data.table::fread(RamenFile)%>%
  as.data.frame()
```
```{r}
View(RamenData)
str(RamenData)
```
##### Where?

##### Who?

##### When & Why

##### What does a case represent? & How may total cases are available?

##### What variables will be using


### Exploration

##### Informative plots

##### Informative statistics

### Preliminary observations & intution 


## 2: Which is the most popular video game?

### Data source
[Video Games Sales with Ratings | Kaggle](https://www.kaggle.com/rush4ratio/video-game-sales-with-ratings)

```{r}
GameFile<- file.choose()
```
```{r}
GameData<- 
  data.table::fread(GameFile)%>%
  as.data.frame()
```
```{r}
View(GameData)
str(GameData)
```

##### Where?

##### Who?

##### When & Why

##### What does a case represent? & How may total cases are available?

##### What variables will be using


### Exploration

##### Informative plots

##### Informative statistics

### Preliminary observations & intution 
